On Developing User Interfaces for Piloting Unmanned Systems

### 2014-02-13 Papers/RSN2014/paper.tex
* Added references to flesh out RSN paper

%---------------------------------------------------------------------%
\section{introduction}

As unmanned aerial vehicles and ground robots become less expensive and more
pervasive, the need for intuitive control interfaces for multiple distributed
systems in environments such as search-and-rescue, resource exploration, and
other situations becomes more pronounced. However, current generations of
interfaces for controlling multiple unmanned systems focus on micro-manipulation
of individual systems within a swarm of autonomous entities. For instance, an
interface for such a grouping of systems may require an operator to select one
or more entities and give them a proximate waypoint, often via GPS, to move to.
Examples of existing systems that do this include the AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner~\cite{arora2013development}; and AFRL's ATAK mission
planning environment~\cite{gillen2012beyond}.
These concepts are extended further in 3D piloting systems based on landmark
navigation~\cite{ranft20133d} and augmented reality~\cite{kochflying}, as
these interfaces tend to require the full attention
of an operator on each UAS, rather than focusing on the group operations.

@@

To understand the benefits of the GAMS interfaces, we must first explore some
of the problems with the state-of-the-art. In this section, we describe some
simple, repeatable experiments with waypoint navigation systems, which as
mentioned in Section~\ref{sec:introduction} are
used in software like AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner~\cite{arora2013development}; and AFRL's ATAK mission planning
environment~\cite{gillen2012beyond}.

@@

The usage of the GAMS interface includes the following steps:
\begin{enumerate}
  \item Select the UAS that will be participating with a box or by list of names
  \item Select an action to perform from a list
  \begin{enumerate}
    \item Primitive operations
    \item Network bridging between two locations
    \item Area coverage
    \item Priority area coverage
  \end{enumerate}
\end{enumerate}

>>>>

%---------------------------------------------------------------------%
\section{sec:introduction}

As unmanned aerial vehicles and ground robots become less expensive and more
pervasive, the need for intuitive control interfaces for multiple distributed
systems in environments such as search-and-rescue, resource exploration, and
other situations becomes more pronounced. However, current generations of
interfaces for controlling multiple unmanned systems focus on micro-manipulation
of individual systems within a swarm of autonomous entities. For instance, an
interface for such a grouping of systems may require an operator to select one
or more entities and give them a proximate waypoint, often via GPS, to move to.
Examples of existing systems that do this include the AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner~\cite{arora2013development}; AFRL's ATAK mission
planning environment~\cite{gillen2012beyond}, and simulation-based flight
systems used as research platforms for UAS~\cite{puls2009gps,chao2007autopilots}.
These concepts are extended further in 3D piloting systems based on landmark
navigation~\cite{ranft20133d} and augmented reality~\cite{kochflying}, as
these interfaces tend to require the full attention
of an operator on each UAS, rather than focusing on the group operations.

@@

To understand the benefits of the GAMS interfaces, we must first explore some
of the problems with the state-of-the-art. In this section, we describe some
simple, repeatable experiments with waypoint navigation systems, such as
those mentioned in Section~\ref{sec:introduction}.

@@

The usage of the GAMS interface includes the following steps:
\begin{enumerate}
  \item Select the UAS that will be participating with a box or by list of names
  \item Select an action to perform from a list
  \begin{enumerate}
    \item Primitive operations
    \item Network bridging between two locations
    \item Area coverage
    \item Priority area coverage
  \end{enumerate}
  \item Select an area and any subareas necessary for the algorithm
\end{enumerate}
